A thermodynamic view of dusty protoplanetary disks

### 2017-05-28 linear.tex
local copy

In Table \ref{si_compare} we also calculate the phase difference
between the Lagragian pressure perturbation and density perturbations
as    
\begin{align*} 
\varphi&\equiv \sgn{\left[\real{(\sigma)}\right]}\arg\left(\Delta
  P\Delta\rho^*\right).\notag 
%\notag\\
%       &= \sgn{\left[\real{(\sigma)}\right]}\arg\left(\Delta\rhog^*\Delta\rhod\right).\notag
\end{align*}
(Note that $\Delta P = \delta P + \ii \dd v_x \p_rP/\sigma$, and it is
important to include the global radial pressure gradient here.) Then 
$\varphi > 0 $ indicates gas pressure lagging behind total density, 
which is true for all the cases. Thus SI is indeed associated with
such a phase lag.

>>>>

In Table \ref{si_compare} we also calculate the phase difference
between the Lagragian pressure perturbation and density perturbations
as    
\begin{align*} 
\varphi&\equiv \sgn{\left[\real{(\sigma)}\right]}\arg\left(\Delta
  P\Delta\rho^*\right).\notag 
%\notag\\
%       &= \sgn{\left[\real{(\sigma)}\right]}\arg\left(\Delta\rhog^*\Delta\rhod\right).\notag
\end{align*}

(Note that $\Delta P = \delta P + \ii \dd v_x \p_rP/\sigma$, and it is
important to include the global radial pressure gradient here.) Then
$\varphi > 0 $ indicates gas pressure lagging behind total density,
which is true for all the cases. Thus SI is indeed associated with
such a phase lag.

In a future work we will perform a detailed comparison between the
simplified one-fluid and full two-fluid frameworks in calculating SI.

\begin{figure}
\includegraphics[width=\linewidth]{figures/si_2f_1f_compare}
\caption{{\bf in case the paper isn't long enough} Comparison of the linear
streaming instability obtained from a full two-fluid analysis and the current 
one-fluid framework simplified by the terminal velocity approximation. The vertical
wavenumber is fixed and growth rates are maximized over $K_x$. 
\label{si_compare_full}}
\end{figure}
%"generalized stokes number" would include other problem parameters,
%e.g. wavenumber
